
The objective of CHORUS would be to create a collaborative,
international development environment for algorithms and tools
designed to harvest information from shared earth observation data
repositories. Sharing applications within this environment has the
following advantages:
\begin{enumerate}
	\item It allows the system to move the code to the data, which
          speeds up the processing, and reduces the cost;
        \item It will enable model testing on private datasets without
	\item It can make the applications available to other clients
          and users;
	\item It encourages collaboration within the CHORUS community,
          possibly including crowd-sourcing.
\end{enumerate}

Tasks will include:
\begin{enumerate}
	\item Developing standard workflow practices: for example,
          users first find data through the use of the catalog API,
          then assign the selected dataset to a working set, and then
          launch individual tasks/algorithms or a chained set of
          tasks/algorithms.
	\item Designing automated and efficient mechanisms to deploy
          algorithms and applications as tasks within the system.
          These would for example take advantage of Hadoop and Spark
          for mass batch processing and analysis.
	\item Automatically selecting CPU or GPU (CUDA) optimized code
          for analysis tasks.
	\item Exploring strategies such as containerized runtime
          virtualization (for example using Docker) to run algorithms
          at scale through the CHORUS environment.
	\item Automating how algorithms can be re-factored for speed,
          for example through feature engineering and with reference
          to the machine learning literature.
	\item Assessing the trade-off space between standardization of
          workflows and optimization of workflows for data throughput,
          with reference to various classes of problems.
	\item Designing and optimizing the user experience for
          interacting with and sharing workflow containers within the
          ecosystem developers and users.
	\item Experimenting with ``cloud sourcing'' of applications.
          This might for example use a revenue-sharing model similar
          to Apple's ``App Store''.
\end{enumerate}

The vision for this project is to provide critical new capabilities
based on what is now redibly available Earth Observation datasets.
The goal is to take CHORUS to a stage where the technology is ready to
be commercialized by industrial partners. Modern constellations of
commercial surveillance satellites that are now being developed are of
great interest to both civilian and defence agencies around the world.
Such constellations will consist of many satellites with frequent
revisit capability and will generate huge amounts of data.  To meet
the requirements of many users, those high volumes of data must first
be translated into geometrically and radiometrically corrected
imagery, analysed to extract the embedded information, and then
delivered around the world in minutes.  This capability can only be
achieved through Cloud Computing on systems such as CHORUS.

This work builds on existing Geospatial Cloud Platforms and tools that
currently enable the ability to generate information products suitable
for such tasks as search and rescue and related defense applications
that include big data analytics applications.  In addition, the IP
that is developed will have high commercialization potential and the
technology will be taken to a stage that it is ready to be
commercialized by industrial partners.


The most critical metric for success will be the engagment factor from
the mulitple stakeholders involved.  If CHORUS is successful, then it
will attract additional datasets, algorithms, and information products
from all of the knowledge domains involved. This method of crowd
sourcing will also identify internationally-important knowledge gaps
and the shared platform will be the foundation upon which we can build
new collaborations.
 
Development of CHORUS will adhere to an Agile Methodology. Agile
iterative approach that builds software incrementally from the start
of the project, instead of trying to deliver a completed platform near
the end of 4 years.  In each iteration, stakeholders will be asked to
come to a consensus on key elements of functionality to support. This
approach will allow the project to most easily adapt to new
opportunities and unexpected challenges.

