We propose to coallesce and leverage existing data sets
using international standards for data interchange to be
shared by several domains of knowledge, including
astrophysics, oceanography, remote sensing, fisheries, emergency
management and robotics. This platform would allow for the exciting
possibility of combining data and algorithms across these different
domains. Example use cases include:
\begin{enumerate}
\item A forest fire-fighter consulting her smartphone before
approaching the fire to see an immersive view of when the fire is at
this moment from near real-time remote sensing combined with GIS
data of the terrain.  Perhaps more importantly, she can also see where
the fire will be in five or ten minutes by harnessing simulations of the
propagation of the fire using the most recent data on the fire, wind
and the forest.
\item The development of a robotic emergency rescue first responder
  equipment through a simulation of the design in the actual terrain
  of interest.  With parallel computation, thousands of potential
  designs could be tested and modified using a genetic algorithm in a
  matter of minutes to find the optimal design.
\item Management of natural resources combined with new techniques
such as fracking combined with climate change, potentially taking into account
the subtle impact on agriculture at a global scale.
\item A public health researcher correlates medical outcomes in a
  private database against geographical data to discover new trends
  underlying disease, without gaining access to any private data.
\end{enumerate}
